04_limma_gon_M

### 2019-04-03 analysis/04_limma_gon_M.Rmd
fixed axis limits

---
title: "04_limma_gon_F"
output: md_document
---

This anlaysis will _exclude_ the control timepoint and will example males and females separately.

@@

knitr::opts_chunk$set(fig.path = '../figures/gon_F/',cache=TRUE)
```

# Females first

@@

```{r filter}
colData <- colData %>%
  dplyr::filter(grepl('gonad', tissue)) %>%
  dplyr::filter(treatment != "control") %>%
  dplyr::filter(sex == "female") %>%
  droplevels()
row.names(colData) <- colData$V1

@@

plotMDS(parentalobject, cex = 0.5, labels = colData$treatment, col=col.treatment)
title("Female Gonad MDS 1v2")
plotMDS(parentalobject, cex = 0.5, labels = colData$treatment, col=col.treatment, dim=c(3,4))
title("Female Gonad MDS 3v4")
plotMDS(parentalobject, cex = 0.5, labels = colData$treatment, col=col.treatment, dim=c(5,6))
title("Female Gonad MDS 5v6")
```

@@

# subset of conrasts - sex specific comparing hatch to lay
my.contrasts <- makeContrasts(
	         FG_BL = female.gonad.bldg - female.gonad.lay,
	         FG_Li3 = female.gonad.lay - female.gonad.inc.d3,
	         FG_i3i9 = female.gonad.inc.d3 - female.gonad.inc.d9,
	         FG_i9i17 = female.gonad.inc.d9 - female.gonad.inc.d17,
	         FG_i17H = female.gonad.inc.d17 - female.gonad.hatch,
	         FG_Hn5 = female.gonad.hatch -  female.gonad.n5,
	         FG_n5n9 = female.gonad.n5 - female.gonad.n9,

	         FG_Bi3 = female.gonad.bldg - female.gonad.inc.d3,
	         FG_Bi9 = female.gonad.bldg - female.gonad.inc.d9,
	         FG_Bi17 = female.gonad.bldg - female.gonad.inc.d17,
	         FG_BH = female.gonad.bldg - female.gonad.hatch,
	         FG_Bn5 = female.gonad.bldg - female.gonad.n5,
	         FG_Bn9 = female.gonad.bldg - female.gonad.n9,

	         FG_Li9 = female.gonad.lay - female.gonad.inc.d9,
           FG_Li17 = female.gonad.lay - female.gonad.inc.d17, 
	         FG_LH = female.gonad.lay - female.gonad.hatch,
	         FG_Ln5 = female.gonad.lay - female.gonad.n5,
	         FG_Ln9 = female.gonad.lay - female.gonad.n9,

	         FG_i3i17 = female.gonad.inc.d3 - female.gonad.inc.d17,
	         FG_i3H = female.gonad.inc.d3 - female.gonad.hatch,
	         FG_i3n5 = female.gonad.inc.d3 - female.gonad.n5,
	         FG_i3n9 = female.gonad.inc.d3 - female.gonad.n9,

	         FG_i9H = female.gonad.inc.d9 - female.gonad.hatch,
	         FG_i9n5 = female.gonad.inc.d9 - female.gonad.n5,
	         FG_i9n9 = female.gonad.inc.d9 - female.gonad.n9,

	         FG_i17n5 = female.gonad.inc.d17 - female.gonad.n5,
	         FG_i17n9 = female.gonad.inc.d17 - female.gonad.n9,

	         FG_Hn9 = female.gonad.hatch -  female.gonad.n9,

@@

for(i in mycontrasts){
  printplotcontrasts(i)
}

```

>>>>

---
title: "04_limma_gon_M"
output: md_document
---

@@

knitr::opts_chunk$set(fig.path = '../figures/gon_M/',cache=TRUE)
```

# Male Gonad Data

This anlaysis will _exclude_ the control timepoint and only examine males.

@@

```{r filter}
colData <- colData %>%
  dplyr::filter(grepl('gonad', tissue)) %>%
  dplyr::filter(treatment != "control") %>%
  dplyr::filter(sex == "male") %>%
  droplevels()
row.names(colData) <- colData$V1

@@

plotMDS(parentalobject, cex = 0.5, labels = colData$treatment, col=col.treatment)
title("Male Gonad MDS 1v2")
plotMDS(parentalobject, cex = 0.5, labels = colData$treatment, col=col.treatment, dim=c(3,4))
title("Male Gonad MDS 3v4")
plotMDS(parentalobject, cex = 0.5, labels = colData$treatment, col=col.treatment, dim=c(5,6))
title("Male Gonad MDS 5v6")
```

@@

# subset of conrasts - sex specific comparing hatch to lay
my.contrasts <- makeContrasts(
	         MG_BL = male.gonad.bldg - male.gonad.lay,
	         MG_Li3 = male.gonad.lay - male.gonad.inc.d3,
	         MG_i3i9 = male.gonad.inc.d3 - male.gonad.inc.d9,
	         MG_i9i17 = male.gonad.inc.d9 - male.gonad.inc.d17,
	         MG_i17H = male.gonad.inc.d17 - male.gonad.hatch,
	         MG_Hn5 = male.gonad.hatch -  male.gonad.n5,
	         MG_n5n9 = male.gonad.n5 - male.gonad.n9,

	         MG_Bi3 = male.gonad.bldg - male.gonad.inc.d3,
	         MG_Bi9 = male.gonad.bldg - male.gonad.inc.d9,
	         MG_Bi17 = male.gonad.bldg - male.gonad.inc.d17,
	         MG_BH = male.gonad.bldg - male.gonad.hatch,
	         MG_Bn5 = male.gonad.bldg - male.gonad.n5,
	         MG_Bn9 = male.gonad.bldg - male.gonad.n9,

	         MG_Li9 = male.gonad.lay - male.gonad.inc.d9,
           MG_Li17 = male.gonad.lay - male.gonad.inc.d17, 
	         MG_LH = male.gonad.lay - male.gonad.hatch,
	         MG_Ln5 = male.gonad.lay - male.gonad.n5,
	         MG_Ln9 = male.gonad.lay - male.gonad.n9,

	         MG_i3i17 = male.gonad.inc.d3 - male.gonad.inc.d17,
	         MG_i3H = male.gonad.inc.d3 - male.gonad.hatch,
	         MG_i3n5 = male.gonad.inc.d3 - male.gonad.n5,
	         MG_i3n9 = male.gonad.inc.d3 - male.gonad.n9,

	         MG_i9H = male.gonad.inc.d9 - male.gonad.hatch,
	         MG_i9n5 = male.gonad.inc.d9 - male.gonad.n5,
	         MG_i9n9 = male.gonad.inc.d9 - male.gonad.n9,

	         MG_i17n5 = male.gonad.inc.d17 - male.gonad.n5,
	         MG_i17n9 = male.gonad.inc.d17 - male.gonad.n9,

	         MG_Hn9 = male.gonad.hatch -  male.gonad.n9,

@@

for(i in mycontrasts){
  printplotcontrasts(i)
}
```
